VariantSpark: Population Scale Clustering of Genotype Information

### 2015-11-20 doc/publications/journal2014/paper.tex
python

\subsection*{Python Implementation}
Our Python implementation reads in lines from a VCF file as tab-separated values and stores the lines in a pandas DataFrame (\url{http://pandas.pydata.org}). The column headings are the individual IDs and the row headings are the allele locations.
We filter out reference-conform data and convert the remaining allele strings to numeric values. 
We cluster this DataFrame using sci-kit learn (\url{http://scikit-learn.org/stable/}), upon converting it to a matrix with {\sc .as\textunderscore{}matrix()}.

>>>>

\subsection*{Python Implementation}
Our Python implementation reads in lines from a VCF file as tab-separated values using {\sc DataFrame.from\textunderscore{}csv}, and stores the data in a pandas DataFrame (\url{http://pandas.pydata.org}). The column headings are the individual IDs and the row headings are the allele locations.
We the first 9 columns and convert the remaining allele strings to numeric values.
We convert the DataFrame to a matrix with {\sc .as\textunderscore{}matrix()} and cluster the matrix using sci-kit learn (\url{http://scikit-learn.org/stable/}).
